Untitled

### 2017-10-02 presentation/transcript_notes.Rmd
transcript done.

>>>>

So a brief summary of the work I've done for my honours research project:
I've explored issues in the Melbourne CBD pedestrian data provided by the City of Melbourne, proposed an algorithm for imputing missings in the data and investigated efficient training model structures within R in this application.
